Limits to detection of early warning signals: Appendices

### 2012-02-16 appendix/appendices.tex
minor edits and touchups

  \begin{abstract}
  These appendices explore several concepts that do not get fully developed in the paper, while also providing an introduction to the early warning signals package we provide to support this paper.  This document is written in Sweave, so the code you see is the code that generates the figures and results shown.   
  \end{abstract}
 \end{frontmatter}

\section{Introduction}
\setkeys{Gin}{width=0.85\textwidth}

@@

Simulate from a system approaching a collapse~64 times,

\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlfunctioncall{require}\hlkeyword{(}\hlsymbol{populationdynamics}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlsymbol{pars}{\ }\hlassignement{=}{\ }\hlfunctioncall{c}\hlkeyword{(}\hlargument{Xo}{\ }\hlargument{=}{\ }\hlnumber{730}\hlkeyword{,}{\ }\hlargument{e}{\ }\hlargument{=}{\ }\hlnumber{0.5}\hlkeyword{,}{\ }\hlargument{a}{\ }\hlargument{=}{\ }\hlnumber{100}\hlkeyword{,}{\ }\hlargument{K}{\ }\hlargument{=}{\ }\hlnumber{1000}\hlkeyword{,}\hspace*{\fill}\\
\hlstd{}{\ }{\ }{\ }{\ }\hlargument{h}{\ }\hlargument{=}{\ }\hlnumber{200}\hlkeyword{,}{\ }\hlargument{i}{\ }\hlargument{=}{\ }\hlnumber{0}\hlkeyword{,}{\ }\hlargument{Da}{\ }\hlargument{=}{\ }\hlnumber{0.09}\hlkeyword{,}{\ }\hlargument{Dt}{\ }\hlargument{=}{\ }\hlnumber{0}\hlkeyword{,}{\ }\hlargument{p}{\ }\hlargument{=}{\ }\hlnumber{2}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlsymbol{time}{\ }\hlassignement{=}{\ }\hlfunctioncall{seq}\hlkeyword{(}\hlnumber{0}\hlkeyword{,}{\ }\hlnumber{900}\hlkeyword{,}{\ }\hlargument{length}{\ }\hlargument{=}{\ }\hlnumber{200}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlsymbol{sn}{\ }\hlassignement{\usebox{\hlnormalsizeboxlessthan}-}{\ }\hlfunctioncall{saddle\usebox{\hlnormalsizeboxunderscore}node\usebox{\hlnormalsizeboxunderscore}ibm}\hlkeyword{(}\hlsymbol{pars}\hlkeyword{,}{\ }\hlsymbol{time}\hlkeyword{,}{\ }\hlargument{reps}{\ }\hlargument{=}{\ }\hlsymbol{nreps}\hlkeyword{)}\mbox{}
\normalfont
\end{flushleft}
\end{kframe}}
\end{knitrout}

We do a little reformatting of the data, 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlsymbol{X}{\ }\hlassignement{\usebox{\hlnormalsizeboxlessthan}-}{\ }\hlfunctioncall{data.frame}\hlkeyword{(}\hlargument{time}{\ }\hlargument{=}{\ }\hlsymbol{time}\hlkeyword{,}{\ }\hlargument{value}{\ }\hlargument{=}{\ }\hlsymbol{sn}\hlkeyword{\usebox{\hlnormalsizeboxdollar}}\hlsymbol{x1}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlsymbol{dat}{\ }\hlassignement{\usebox{\hlnormalsizeboxlessthan}-}{\ }\hlfunctioncall{melt}\hlkeyword{(}\hlsymbol{X}\hlkeyword{,}{\ }\hlargument{id}{\ }\hlargument{=}{\ }\hlstring{"{}time"{}}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlfunctioncall{names}\hlkeyword{(}\hlsymbol{dat}\hlkeyword{)}\hlkeyword{[}\hlnumber{2}\hlkeyword{]}{\ }\hlassignement{\usebox{\hlnormalsizeboxlessthan}-}{\ }\hlstring{"{}reps"{}}\mbox{}
\normalfont
\end{flushleft}
\end{kframe}}
\end{knitrout}

and compute the autocorrelation over a window in time equal half the length if the timeseries
\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlsymbol{acorr}{\ }\hlassignement{\usebox{\hlnormalsizeboxlessthan}-}{\ }\hlfunctioncall{summary\usebox{\hlnormalsizeboxunderscore}statistic}\hlkeyword{(}\hlsymbol{dat}\hlkeyword{,}{\ }\hlsymbol{window\usebox{\hlnormalsizeboxunderscore}autocorr}\hlkeyword{,}\hspace*{\fill}\\
\hlstd{}{\ }{\ }{\ }{\ }\hlargument{windowsize}{\ }\hlargument{=}{\ }\hlfunctioncall{length}\hlkeyword{(}\hlsymbol{time}\hlkeyword{)}\hlkeyword{/}\hlnumber{2}\hlkeyword{)}\mbox{}
\normalfont
\end{flushleft}
\end{kframe}}
\end{knitrout}

\begin{figure}[H]
\begin{center}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlfunctioncall{ggplot}\hlkeyword{(}\hlsymbol{acorr}\hlkeyword{)}{\ }\hlkeyword{+}{\ }\hlfunctioncall{geom\usebox{\hlnormalsizeboxunderscore}line}\hlkeyword{(}\hlfunctioncall{aes}\hlkeyword{(}\hlsymbol{time}\hlkeyword{,}{\ }\hlsymbol{value}\hlkeyword{)}\hlkeyword{)}{\ }\hlkeyword{+}\hspace*{\fill}\\
\hlstd{}{\ }{\ }{\ }{\ }\hlfunctioncall{facet\usebox{\hlnormalsizeboxunderscore}wrap}\hlkeyword{(}\hlkeyword{\urltilda{}}\hlsymbol{reps}\hlkeyword{)}{\ }\hlkeyword{+}{\ }\hlfunctioncall{opts}\hlkeyword{(}\hlargument{title}{\ }\hlargument{=}{\ }\hlstring{"{}Autocorrelation{\ }on{\ }replicates{\ }from{\ }a{\ }system{\ }approaching{\ }a{\ }crash"{}}\hlkeyword{)}\mbox{}
\normalfont
\end{flushleft}

@@

\caption{The pattern of autocorrelation in replicate simulations from a simulation of a system which is approaching a saddle node bifurcation.}\label{crashacor}
\end{center}
\end{figure}

@@

We provide the code in this document to both illustrate the steps required and also that the commands can be copy-pasted into R using different choices for the warning indicator, the sampling of the simulation, etc.

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlfunctioncall{require}\hlkeyword{(}\hlsymbol{snowfall}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlfunctioncall{sfInit}\hlkeyword{(}\hlargument{par}{\ }\hlargument{=}{\ }\hlsymbol{T}\hlkeyword{,}{\ }\hlargument{cpu}{\ }\hlargument{=}{\ }\hlnumber{16}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlfunctioncall{sfLibrary}\hlkeyword{(}\hlsymbol{earlywarning}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlfunctioncall{sfExportAll}\hlkeyword{(}\hlkeyword{)}\mbox{}
\normalfont
\end{flushleft}
\end{kframe}}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlsymbol{reps}{\ }\hlassignement{\usebox{\hlnormalsizeboxlessthan}-}{\ }\hlfunctioncall{sfLapply}\hlkeyword{(}\hlnumber{1}\hlkeyword{:}\hlnumber{500}\hlkeyword{,}{\ }\hlkeyword{function}\hlkeyword{(}\hlformalargs{i}\hlkeyword{)}{\ }\hlfunctioncall{compare}\hlkeyword{(}\hlsymbol{A}\hlkeyword{,}\hspace*{\fill}\\
\hlstd{}{\ }{\ }{\ }{\ }\hlsymbol{B}\hlkeyword{)}\hlkeyword{)}\mbox{}
\normalfont
\end{flushleft}
\end{kframe}}
\end{knitrout}

@@

\begin{figure}[H]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlfunctioncall{require}\hlkeyword{(}\hlsymbol{ggplot2}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlfunctioncall{ggplot}\hlkeyword{(}\hlsymbol{lr}\hlkeyword{)}{\ }\hlkeyword{+}{\ }\hlfunctioncall{geom\usebox{\hlnormalsizeboxunderscore}density}\hlkeyword{(}\hlfunctioncall{aes}\hlkeyword{(}\hlsymbol{value}\hlkeyword{,}{\ }\hlargument{fill}{\ }\hlargument{=}{\ }\hlsymbol{simulation}\hlkeyword{)}\hlkeyword{,}\hspace*{\fill}\\
\hlstd{}{\ }{\ }{\ }{\ }\hlargument{alpha}{\ }\hlargument{=}{\ }\hlnumber{0.7}\hlkeyword{)}{\ }\hlkeyword{+}{\ }\hlfunctioncall{geom\usebox{\hlnormalsizeboxunderscore}vline}\hlkeyword{(}\hlargument{xintercept}{\ }\hlargument{=}{\ }\hlsymbol{observed}\hlkeyword{,}{\ }\hlargument{lty}{\ }\hlargument{=}{\ }\hlnumber{2}\hlkeyword{)}\mbox{}
\normalfont
\end{flushleft}

@@

\begin{figure}[H]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlfunctioncall{require}\hlkeyword{(}\hlsymbol{beanplot}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlfunctioncall{beanplot}\hlkeyword{(}\hlsymbol{value}{\ }\hlkeyword{\urltilda{}}{\ }\hlsymbol{simulation}\hlkeyword{,}{\ }\hlsymbol{lr}\hlkeyword{,}{\ }\hlargument{what}{\ }\hlargument{=}{\ }\hlfunctioncall{c}\hlkeyword{(}\hlnumber{0}\hlkeyword{,}{\ }\hlnumber{1}\hlkeyword{,}\hspace*{\fill}\\
\hlstd{}{\ }{\ }{\ }{\ }\hlnumber{0}\hlkeyword{,}{\ }\hlnumber{0}\hlkeyword{)}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlfunctioncall{abline}\hlkeyword{(}\hlargument{h}{\ }\hlargument{=}{\ }\hlsymbol{observed}\hlkeyword{,}{\ }\hlargument{lty}{\ }\hlargument{=}{\ }\hlnumber{2}\hlkeyword{)}\mbox{}
\normalfont
\end{flushleft}

@@

\begin{figure}[H]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlsymbol{roc}{\ }\hlassignement{\usebox{\hlnormalsizeboxlessthan}-}{\ }\hlfunctioncall{roc\usebox{\hlnormalsizeboxunderscore}data}\hlkeyword{(}\hlsymbol{lr}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlfunctioncall{ggplot}\hlkeyword{(}\hlsymbol{roc}\hlkeyword{)}{\ }\hlkeyword{+}{\ }\hlfunctioncall{geom\usebox{\hlnormalsizeboxunderscore}line}\hlkeyword{(}\hlfunctioncall{aes}\hlkeyword{(}\hlsymbol{False.positives}\hlkeyword{,}{\ }\hlsymbol{True.positives}\hlkeyword{)}\hlkeyword{,}\hspace*{\fill}\\
\hlstd{}{\ }{\ }{\ }{\ }\hlargument{lwd}{\ }\hlargument{=}{\ }\hlnumber{1}\hlkeyword{)}\mbox{}
\normalfont
\end{flushleft}

@@

\begin{figure}[H]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlfunctioncall{require}\hlkeyword{(}\hlsymbol{Hmisc}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlfunctioncall{ggplot}\hlkeyword{(}\hlfunctioncall{subset}\hlkeyword{(}\hlsymbol{pars}\hlkeyword{,}{\ }\hlsymbol{fit}{\ }\hlkeyword{\usebox{\hlnormalsizeboxpercent}in\usebox{\hlnormalsizeboxpercent}}{\ }\hlfunctioncall{c}\hlkeyword{(}\hlstring{"{}AA"{}}\hlkeyword{,}{\ }\hlstring{"{}BB"{}}\hlkeyword{)}\hlkeyword{)}\hlkeyword{,}{\ }\hlfunctioncall{aes}\hlkeyword{(}\hlsymbol{fit}\hlkeyword{,}\hspace*{\fill}\\
\hlstd{}{\ }{\ }{\ }{\ }\hlsymbol{value}\hlkeyword{)}\hlkeyword{)}{\ }\hlkeyword{+}{\ }\hlfunctioncall{stat\usebox{\hlnormalsizeboxunderscore}summary}\hlkeyword{(}\hlargument{fun.y}{\ }\hlargument{=}{\ }\hlsymbol{mean}\hlkeyword{,}{\ }\hlargument{geom}{\ }\hlargument{=}{\ }\hlstring{"{}bar"{}}\hlkeyword{,}{\ }\hlargument{position}{\ }\hlargument{=}{\ }\hlstring{"{}dodge"{}}\hlkeyword{)}{\ }\hlkeyword{+}\hspace*{\fill}\\
\hlstd{}{\ }{\ }{\ }{\ }\hlfunctioncall{stat\usebox{\hlnormalsizeboxunderscore}summary}\hlkeyword{(}\hlargument{fun.data}{\ }\hlargument{=}{\ }\hlsymbol{median\usebox{\hlnormalsizeboxunderscore}hilow}\hlkeyword{,}{\ }\hlargument{geom}{\ }\hlargument{=}{\ }\hlstring{"{}pointrange"{}}\hlkeyword{,}\hspace*{\fill}\\
\hlstd{}{\ }{\ }{\ }{\ }{\ }{\ }{\ }{\ }\hlargument{position}{\ }\hlargument{=}{\ }\hlfunctioncall{position\usebox{\hlnormalsizeboxunderscore}dodge}\hlkeyword{(}\hlargument{width}{\ }\hlargument{=}{\ }\hlnumber{0.9}\hlkeyword{)}\hlkeyword{,}{\ }\hlargument{conf.int}{\ }\hlargument{=}{\ }\hlnumber{0.95}\hlkeyword{)}{\ }\hlkeyword{+}\hspace*{\fill}\\
\hlstd{}{\ }{\ }{\ }{\ }\hlfunctioncall{facet\usebox{\hlnormalsizeboxunderscore}wrap}\hlkeyword{(}\hlkeyword{\urltilda{}}\hlsymbol{parameter}\hlkeyword{,}{\ }\hlargument{scales}{\ }\hlargument{=}{\ }\hlstring{"{}free\usebox{\hlnormalsizeboxunderscore}y"{}}\hlkeyword{)}\mbox{}
\normalfont
\end{flushleft}

@@

\subsection{Visualizing the simulation replicates}

The \texttt{reps} list also contains the simulation data from each replicate

\begin{figure}[H]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlsymbol{sims}{\ }\hlassignement{\usebox{\hlnormalsizeboxlessthan}-}{\ }\hlfunctioncall{get\usebox{\hlnormalsizeboxunderscore}replicates}\hlkeyword{(}\hlsymbol{reps}\hlkeyword{)}\mbox{}
\normalfont
\end{flushleft}
\begin{verbatim}
## Error: argument is of length zero
\end{verbatim}
\begin{flushleft}
\ttfamily\noindent
\hlfunctioncall{ggplot}\hlkeyword{(}\hlsymbol{sims}\hlkeyword{)}{\ }\hlkeyword{+}{\ }\hlfunctioncall{geom\usebox{\hlnormalsizeboxunderscore}line}\hlkeyword{(}\hlfunctioncall{aes}\hlkeyword{(}\hlsymbol{time}\hlkeyword{,}{\ }\hlsymbol{value}\hlkeyword{,}{\ }\hlargument{group}{\ }\hlargument{=}{\ }\hlsymbol{rep}\hlkeyword{)}\hlkeyword{,}\hspace*{\fill}\\
\hlstd{}{\ }{\ }{\ }{\ }\hlargument{alpha}{\ }\hlargument{=}{\ }\hlnumber{0.1}\hlkeyword{)}{\ }\hlkeyword{+}{\ }\hlfunctioncall{facet\usebox{\hlnormalsizeboxunderscore}wrap}\hlkeyword{(}\hlkeyword{\urltilda{}}\hlsymbol{model}\hlkeyword{)}\mbox{}
\normalfont
\end{flushleft}
\begin{verbatim}
## Error: object 'sims' not found
\end{verbatim}
\end{kframe}}
\end{knitrout}

>>>>

  \begin{abstract}
  These appendices explore several concepts that do not get fully developed in the paper, while also providing an introduction to the early warning signals package we provide (\href{https://github.com/cboettig/earlywarning}{https://github.com/cboettig/earlywarning}) to support this paper.  We provide the code in this document to both illustrate the steps required and also that the commands can be copy-pasted into~\texttt{R} using different choices for the warning indicator, the sampling of the simulation, etc.  This document is written in Sweave, so the code you see is the code that generates the figures and results shown.   
  \end{abstract}
 \end{frontmatter}

\section{Introduction -- Visualizing early warning patterns}
\setkeys{Gin}{width=0.95\textwidth}

@@

Simulate from a system approaching a collapse~64 times using our population dynamics package, available at \href{https://github.com/cboettig/populationdynamics}{https://github.com/cboettig/populationdynamics},

\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlfunctioncall{require}\hlkeyword{(}\hlsymbol{populationdynamics}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlsymbol{pars}{\ }\hlassignement{=}{\ }\hlfunctioncall{c}\hlkeyword{(}\hlargument{Xo}{\ }\hlargument{=}{\ }\hlnumber{730}\hlkeyword{,}{\ }\hlargument{e}{\ }\hlargument{=}{\ }\hlnumber{0.5}\hlkeyword{,}{\ }\hlargument{a}{\ }\hlargument{=}{\ }\hlnumber{100}\hlkeyword{,}{\ }\hlargument{K}{\ }\hlargument{=}{\ }\hlnumber{1000}\hlkeyword{,}{\ }\hlargument{h}{\ }\hlargument{=}{\ }\hlnumber{200}\hlkeyword{,}{\ }\hlargument{i}{\ }\hlargument{=}{\ }\hlnumber{0}\hlkeyword{,}{\ }\hlargument{Da}{\ }\hlargument{=}{\ }\hlnumber{.09}\hlkeyword{,}{\ }\hlargument{Dt}{\ }\hlargument{=}{\ }\hlnumber{0}\hlkeyword{,}{\ }\hlargument{p}{\ }\hlargument{=}{\ }\hlnumber{2}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlsymbol{time}\hlassignement{=}\hlfunctioncall{seq}\hlkeyword{(}\hlnumber{0}\hlkeyword{,}{\ }\hlnumber{900}\hlkeyword{,}{\ }\hlargument{length}\hlargument{=}\hlnumber{200}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlsymbol{sn}{\ }\hlassignement{\usebox{\hlnormalsizeboxlessthan}-}{\ }\hlfunctioncall{saddle\usebox{\hlnormalsizeboxunderscore}node\usebox{\hlnormalsizeboxunderscore}ibm}\hlkeyword{(}\hlsymbol{pars}\hlkeyword{,}\hlsymbol{time}\hlkeyword{,}{\ }\hlargument{reps}\hlargument{=}\hlsymbol{nreps}\hlkeyword{)}\mbox{}
\normalfont
\end{flushleft}
\end{kframe}}
\end{knitrout}

We do a little reformatting of the data, 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlsymbol{X}{\ }\hlassignement{\usebox{\hlnormalsizeboxlessthan}-}{\ }\hlfunctioncall{data.frame}\hlkeyword{(}\hlargument{time}\hlargument{=}\hlsymbol{time}\hlkeyword{,}{\ }\hlargument{value}\hlargument{=}\hlsymbol{sn}\hlkeyword{\usebox{\hlnormalsizeboxdollar}}\hlsymbol{x1}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlsymbol{dat}{\ }\hlassignement{\usebox{\hlnormalsizeboxlessthan}-}{\ }\hlfunctioncall{melt}\hlkeyword{(}\hlsymbol{X}\hlkeyword{,}{\ }\hlargument{id}\hlargument{=}\hlstring{"{}time"{}}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlfunctioncall{names}\hlkeyword{(}\hlsymbol{dat}\hlkeyword{)}\hlkeyword{[}\hlnumber{2}\hlkeyword{]}{\ }\hlassignement{\usebox{\hlnormalsizeboxlessthan}-}{\ }\hlstring{"{}reps"{}}\mbox{}
\normalfont
\end{flushleft}
\end{kframe}}
\end{knitrout}

and compute the autocorrelation over a window in time equal half the length if the timeseries
\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlsymbol{acorr}{\ }\hlassignement{\usebox{\hlnormalsizeboxlessthan}-}{\ }\hlfunctioncall{summary\usebox{\hlnormalsizeboxunderscore}statistic}\hlkeyword{(}\hlsymbol{dat}\hlkeyword{,}{\ }\hlsymbol{window\usebox{\hlnormalsizeboxunderscore}autocorr}\hlkeyword{,}{\ }\hlargument{windowsize}\hlargument{=}\hlfunctioncall{length}\hlkeyword{(}\hlsymbol{time}\hlkeyword{)}\hlkeyword{/}\hlnumber{2}\hlkeyword{)}\mbox{}
\normalfont
\end{flushleft}
\end{kframe}}
\end{knitrout}

\setkeys{Gin}{width=0.95\textwidth}

\begin{figure}[H]
\begin{center}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlfunctioncall{ggplot}\hlkeyword{(}\hlsymbol{acorr}\hlkeyword{)}{\ }\hlkeyword{+}{\ }\hlfunctioncall{geom\usebox{\hlnormalsizeboxunderscore}line}\hlkeyword{(}\hlfunctioncall{aes}\hlkeyword{(}\hlsymbol{time}\hlkeyword{,}{\ }\hlsymbol{value}\hlkeyword{)}\hlkeyword{)}{\ }\hlkeyword{+}{\ }\hlfunctioncall{facet\usebox{\hlnormalsizeboxunderscore}wrap}\hlkeyword{(}\hlkeyword{\urltilda{}}\hlsymbol{reps}\hlkeyword{)}{\ }\hlkeyword{+}\hspace*{\fill}\\
\hlstd{}{\ }{\ }\hlfunctioncall{opts}\hlkeyword{(}\hlargument{title}\hlargument{=}\hlstring{"{}Autocorrelation{\ }on{\ }replicates{\ }from{\ }a{\ }system{\ }approaching{\ }a{\ }crash"{}}\hlkeyword{)}\mbox{}
\normalfont
\end{flushleft}

@@

\caption{The pattern of autocorrelation in replicate simulations from a simulation of a system which is approaching a saddle node bifurcation.  While a defintitive trend is occassionally visible, clearly we will statistical methods to define what constitutes an "increase."  Our model-based toolset provides this.}\label{crashacor}
\end{center}
\end{figure}
\setkeys{Gin}{width=0.5\textwidth}

@@

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlfunctioncall{require}\hlkeyword{(}\hlsymbol{snowfall}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlfunctioncall{sfInit}\hlkeyword{(}\hlargument{par}\hlargument{=}\hlsymbol{T}\hlkeyword{,}{\ }\hlargument{cpu}\hlargument{=}\hlnumber{16}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlfunctioncall{sfLibrary}\hlkeyword{(}\hlsymbol{earlywarning}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlfunctioncall{sfExportAll}\hlkeyword{(}\hlkeyword{)}\mbox{}
\normalfont
\end{flushleft}
\end{kframe}}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlsymbol{reps}{\ }\hlassignement{\usebox{\hlnormalsizeboxlessthan}-}{\ }\hlfunctioncall{sfLapply}\hlkeyword{(}\hlnumber{1}\hlkeyword{:}\hlnumber{500}\hlkeyword{,}{\ }\hlkeyword{function}\hlkeyword{(}\hlformalargs{i}\hlkeyword{)}{\ }\hlfunctioncall{compare}\hlkeyword{(}\hlsymbol{A}\hlkeyword{,}\hlsymbol{B}\hlkeyword{)}\hlkeyword{)}\mbox{}
\normalfont
\end{flushleft}
\end{kframe}}
\end{knitrout}

@@

\begin{figure}[H]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlfunctioncall{require}\hlkeyword{(}\hlsymbol{ggplot2}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlfunctioncall{ggplot}\hlkeyword{(}\hlsymbol{lr}\hlkeyword{)}{\ }\hlkeyword{+}{\ }\hlfunctioncall{geom\usebox{\hlnormalsizeboxunderscore}density}\hlkeyword{(}\hlfunctioncall{aes}\hlkeyword{(}\hlsymbol{value}\hlkeyword{,}{\ }\hlargument{fill}\hlargument{=}\hlsymbol{simulation}\hlkeyword{)}\hlkeyword{,}{\ }\hlargument{alpha}\hlargument{=}\hlnumber{.7}\hlkeyword{)}{\ }\hlkeyword{+}\hspace*{\fill}\\
\hlstd{}{\ }{\ }\hlfunctioncall{geom\usebox{\hlnormalsizeboxunderscore}vline}\hlkeyword{(}\hlargument{xintercept}\hlargument{=}\hlsymbol{observed}\hlkeyword{,}{\ }\hlargument{lty}\hlargument{=}\hlnumber{2}\hlkeyword{)}\mbox{}
\normalfont
\end{flushleft}

@@

\begin{figure}[H]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlfunctioncall{require}\hlkeyword{(}\hlsymbol{beanplot}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlfunctioncall{beanplot}\hlkeyword{(}\hlsymbol{value}{\ }\hlkeyword{\urltilda{}}{\ }\hlsymbol{simulation}\hlkeyword{,}{\ }\hlsymbol{lr}\hlkeyword{,}{\ }\hlargument{what}\hlargument{=}\hlfunctioncall{c}\hlkeyword{(}\hlnumber{0}\hlkeyword{,}\hlnumber{1}\hlkeyword{,}\hlnumber{0}\hlkeyword{,}\hlnumber{0}\hlkeyword{)}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlfunctioncall{abline}\hlkeyword{(}\hlargument{h}\hlargument{=}\hlsymbol{observed}\hlkeyword{,}{\ }\hlargument{lty}\hlargument{=}\hlnumber{2}\hlkeyword{)}\mbox{}
\normalfont
\end{flushleft}

@@

\begin{figure}[H]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlsymbol{roc}{\ }\hlassignement{\usebox{\hlnormalsizeboxlessthan}-}{\ }\hlfunctioncall{roc\usebox{\hlnormalsizeboxunderscore}data}\hlkeyword{(}\hlsymbol{lr}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlfunctioncall{ggplot}\hlkeyword{(}\hlsymbol{roc}\hlkeyword{)}{\ }\hlkeyword{+}{\ }\hlfunctioncall{geom\usebox{\hlnormalsizeboxunderscore}line}\hlkeyword{(}\hlfunctioncall{aes}\hlkeyword{(}\hlsymbol{False.positives}\hlkeyword{,}{\ }\hlsymbol{True.positives}\hlkeyword{)}\hlkeyword{,}{\ }\hlargument{lwd}\hlargument{=}\hlnumber{1}\hlkeyword{)}\mbox{}
\normalfont
\end{flushleft}

@@

\begin{figure}[H]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{.97, .97, .97}{\color{fgcolor}\begin{kframe}
\begin{flushleft}
\ttfamily\noindent
\hlfunctioncall{require}\hlkeyword{(}\hlsymbol{Hmisc}\hlkeyword{)}\hspace*{\fill}\\
\hlstd{}\hlfunctioncall{ggplot}\hlkeyword{(}\hlfunctioncall{subset}\hlkeyword{(}\hlsymbol{pars}\hlkeyword{,}{\ }\hlsymbol{fit}{\ }\hlkeyword{\usebox{\hlnormalsizeboxpercent}in\usebox{\hlnormalsizeboxpercent}}{\ }\hlfunctioncall{c}\hlkeyword{(}\hlstring{"{}AA"{}}\hlkeyword{,}{\ }\hlstring{"{}BB"{}}\hlkeyword{)}\hlkeyword{)}\hlkeyword{,}{\ }\hlfunctioncall{aes}\hlkeyword{(}\hlsymbol{fit}\hlkeyword{,}{\ }\hlsymbol{value}\hlkeyword{)}\hlkeyword{)}{\ }\hlkeyword{+}\hspace*{\fill}\\
\hlstd{}{\ }{\ }\hlfunctioncall{stat\usebox{\hlnormalsizeboxunderscore}summary}\hlkeyword{(}\hlargument{fun.y}{\ }\hlargument{=}{\ }\hlsymbol{mean}\hlkeyword{,}{\ }\hlargument{geom}{\ }\hlargument{=}{\ }\hlstring{"{}bar"{}}\hlkeyword{,}{\ }\hlargument{position}{\ }\hlargument{=}{\ }\hlstring{"{}dodge"{}}\hlkeyword{)}{\ }\hlkeyword{+}\hspace*{\fill}\\
\hlstd{}{\ }{\ }\hlfunctioncall{stat\usebox{\hlnormalsizeboxunderscore}summary}\hlkeyword{(}\hlargument{fun.data}{\ }\hlargument{=}{\ }\hlsymbol{median\usebox{\hlnormalsizeboxunderscore}hilow}\hlkeyword{,}{\ }\hlargument{geom}{\ }\hlargument{=}{\ }\hlstring{"{}pointrange"{}}\hlkeyword{,}\hspace*{\fill}\\
\hlstd{}{\ }{\ }{\ }{\ }{\ }{\ }{\ }{\ }{\ }{\ }{\ }{\ }{\ }{\ }{\ }\hlargument{position}{\ }\hlargument{=}{\ }\hlfunctioncall{position\usebox{\hlnormalsizeboxunderscore}dodge}\hlkeyword{(}\hlargument{width}{\ }\hlargument{=}{\ }\hlnumber{0.90}\hlkeyword{)}\hlkeyword{,}{\ }\hlargument{conf.int}{\ }\hlargument{=}{\ }\hlnumber{0.95}\hlkeyword{)}{\ }\hlkeyword{+}\hspace*{\fill}\\
\hlstd{}{\ }{\ }\hlfunctioncall{facet\usebox{\hlnormalsizeboxunderscore}wrap}\hlkeyword{(}\hlkeyword{\urltilda{}}\hlsymbol{parameter}\hlkeyword{,}{\ }\hlargument{scales}\hlargument{=}\hlstring{"{}free\usebox{\hlnormalsizeboxunderscore}y"{}}\hlkeyword{)}\mbox{}
\normalfont
\end{flushleft}

@@

%\subsection{Visualizing the simulation replicates}
%
%The \texttt{reps} list also contains the simulation data from each replicate
%\setkeys{Gin}{width=0.95\textwidth}
%
%\begin{figure}[H]
%<<<repsplot, fig.width=7>>=
%sims <- get_replicates(reps)
%ggplot(sims) + geom_line(aes(time, value, group=rep), alpha=0.1) + facet_wrap(~model)
%@
%\end{figure}
%\setkeys{Gin}{width=0.5\textwidth}
